Mapping the current knowledge in syndemic research applied to Men who have Sex with Men: a Scoping Review

### 2022-04-22 _bookdown_files/03-methodology.Rmd
Revisions

The complete protocol of this scoping review was published in 2020 [Author (2020 of publication) Details omitted for double-blind review.].

@@

Screening and data charting were completed using DistillerSR (Evidence Partners, Ottawa, Canada). Scripts, statistics, charts, tables and the present paper was generated using R [@rcoreteam2020], RStudio [@rstudioteam2020] and the appropriate packages. To ensure the complete transparency and reproducibility of this article, the lead author (M.O.) uploaded all data used to generate this article on Open Science Framework ([[DOI:[masked](DOI:%5Bmasked](DOI:%5Bmasked%5D(DOI:%5Bmasked)%7B.uri%7D){.uri} for the anonymity of the review])

>>>>

The complete protocol of this scoping review was published in 2020 (Author, 2020. Details omitted for double-blind review).

@@

Screening and data charting were completed using DistillerSR (Evidence Partners, Ottawa, Canada). Scripts, statistics, charts, tables and the present paper was generated using R [@rcoreteam2020], RStudio [@rstudioteam2020] and the appropriate packages. To ensure the complete transparency and reproducibility of this article, the lead author uploaded all data used to generate this article on Open Science Framework ([DOI: masked for the anonymity of the review])
